---
title: "TraitMatching"
author: "Maximilian Pichler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TraitMatching}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r,eval=FALSE}
library(TraitMatching)
```


## Simulation:
First, let's simulate two groups of species (e.g. plants and pollinators) with one trait-matching effect: Trait A1 - Trait B1.

```{r,eval=FALSE}
# We set species abundances (which is passed to createSpecies) to false.
species = simulateInteraction(inter = matrix(c("A1", "B1"), nrow = 1L), weights = list(main = 0, inter = 10),setSeed = 42, abundance = FALSE)
```

We have to transform our three matrices into a community object with the createCommunity function. Here, you can replace the simulated data with your empiricial data. The minOneInter function trims our interaction matrix z because probably we observe only species that interaction at least once:
```{r,eval=FALSE}
community = createCommunity(species$A, species$B, minOneInter(species$binar(0.3))) # binar for 0/1 interactions, we have to provide an observation time value, the longer we observe the network, the more interactions we will observe.
summary(community$data)
```


## Fit model
Default is hyperparameter tuning with nested CV. Tuning is parallelized. You can train more than one model at the same time. Over and Undersampling are also supported (see help). TraitMatching package relies on the mlr framework. So in the following we will use mlr functions for handling the models:

```{r,eval=FALSE,fig.show='hold'}
results = runTM(community, iters = 5L, parallel = 5L, 
                crossValidation = list(outer = list(method = "CV", iters = 3), inner = list(method = "CV", iters = 3)))
print(results)

```

## Check tune results
```{r,eval=FALSE}
print(results$Result$RF$result$extract[[1]])
print(results$Result$RF$result$extract[[2]])
```

## Get ranger model:
```{r,eval=FALSE}
rf = getLearnerModel(results$Result$RF$result$models[[1]], more.unwrap = TRUE)

```

## Calculate trait-matching effects from fitted models
```{r,eval=FALSE}
tm_effect = get_Interaction_Strengths(community$data[,-c(1,2)], model = results$Result$RF$result$models[[1]], 
                                      any = FALSE, target = "target", grid_size = 15L, any_n_times = 1L,
                                      depth = 5L,  groups = c("A", "B"), parallel = 5L)

print(tm_effect$pairwise_interactions)
```

