---
# title: "PredictionSimulation"
# author: "Maximilian Pichler"
# date: "26 August 2018"
documentclass: report
fontsize: 11pt
output:
  pdf_document: 
    highlight: monochrome
  html_document: 
    keep_md: yes
    
    
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,warning = FALSE, error = F,tidy.opts=list(width.cutoff=40),tidy=TRUE , tidy = TRUE,size = "tiny")
hook_output = knitr::knit_hooks$get('output')
knitr::knit_hooks$set(output = function(x, options) {
  if (!is.null(n<- options$linewidth)) {
    x = knitr:::split_lines(x)
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```
# Simulated plant-pollinator networks
## Run Simulation for comparing predictive performance

```{r, results = FALSE}
library(TraitMatching)
library(mlr)
oldpar = par()
reset = function() suppressWarnings(do.call(par, oldpar))
run =TRUE
set.seed(42)
```


```{r, echo=FALSE}
df = data.frame("Trait Interaction" = c("A1 + B2", "A2 + B3", "A3 + B4"), 
                "Type" = c("continuous + continuous", "continuous + continuous", "continuous + continuous"))
knitr::kable(df,caption = "Simulated trait combinations")
```

## meta parameter
```{r}
epochs = 50L
iter = 30
parallel = 10L
run = TRUE
crossValidation = list(outer = list(method = "SpCV", iters = 5, predict = "both"), 
                                 inner = list(method = "SpCV", iters = 3))


run = TRUE
```

### Without effects and abundances - baseline
- wide and weak effects (gaussian with sd = 100)
- no species abundances
- 50*100 base network size
```{r,results=FALSE}
set.seed(42)
simulatedData = simulateInteraction(main = NULL, inter = matrix(c("A1", "B1"), ncol = 2, byrow = T),
                              weights = list(inter = 1),
                              NumberA = 50, NumberB = 100, traitsA = c(0,6), 
                              traitsB = c(0,6),abundance = FALSE, specRange = c(100,100))
table(as.matrix(minOneInter(simulatedData$binar(3e2))))
```

```{r, results=FALSE}
resultBaselineC = runTM(createCommunity(simulatedData$A, simulatedData$B, minOneInter(simulatedData$binar(3e2))), 
                         method = c( "glm", "glm_step"), 
          settings = list(dnn = list(seed = 42,  activation = "relu", drop = 0.2, archFunction = "continous", epochs = epochs),
                          cnn = list(seed = 42, activation = "relu", 
                                     drop = 0.2, nConv = 1, archFunction = "continous", epochs = epochs)),
                       tune = "random", iters = iter,  fitSpecies = F,
                       crossValidation = crossValidation, 
                       balanceClasses = "None", block = T, parallel = parallel, seed = 42, keepModels = T)
    saveRDS(resultBaselineC, file = "Results/simBaselineC_GLM.RDS")

resultBaselineR = runTM(createCommunity(simulatedData$A, simulatedData$B, minOneInter(simulatedData$poisson(3e2)),log = FALSE ), 
                         method =  c( "glm", "glm_step"), 
          settings = list(negBin = list(seed = 42, batch = 50, 
                                        distribution = "poisson",  archFunction = "continous", epochs = epochs),
                          boost = list( objective = "count:poisson"),
                          glm = list(family = "poisson"),
                          glm_step = list(family = "poisson")),
                       tune = "random", iters = iter,  fitSpecies = F,
                       crossValidation = crossValidation, tuningMetric = "spearmanrho",
                       balanceClasses = "None", block = T, parallel = parallel, seed = 42, keepModels = T)
    saveRDS(resultBaselineR, file = "Results/simBaselineR_GLM.RDS")
```

### Without effects but with abundances - baseline with abundances
- wide and weak effects (gaussian with sd = 100)
- species abundances
- 50*100 base network size
```{r,results=FALSE}
set.seed(42)
simulatedData = simulateInteraction(main = NULL, inter = matrix(c("A1", "B1"), ncol = 2, byrow = T),
                              weights = list(inter = 1),
                              NumberA = 50, NumberB = 100, traitsA = c(0,6), 
                              traitsB = c(0,6),abundance = function(a,b) return(rexp(a, 2)), specRange = c(100,100))
table(as.matrix(minOneInter(simulatedData$binar(4e3))))
```
```{r, results=FALSE}
resultAbC = runTM(createCommunity(simulatedData$A, simulatedData$B, minOneInter(simulatedData$binar(4e3))), 
                         method =  c( "glm", "glm_step"), 
          settings = list(dnn = list(seed = 42,  activation = "relu", drop = 0.2, archFunction = "continous", epochs = epochs),
                          cnn = list(seed = 42, activation = "relu", 
                                     drop = 0.2, nConv = 1, archFunction = "continous", epochs = epochs)),
                       tune = "random", iters = iter,  fitSpecies = F,
                       crossValidation = crossValidation, 
                       balanceClasses = "None", block = T, parallel = parallel, seed = 42, keepModels = T)
    saveRDS(resultAbC, file = "Results/simAbC_GLM.RDS")
    
resultAbR = runTM(createCommunity(simulatedData$A, simulatedData$B, minOneInter(simulatedData$poisson(4e3)),log = FALSE), 
                         method =  c( "glm", "glm_step"),  
          settings = list(negBin = list(seed = 42,  batch = 50, 
                                        distribution = "poisson",  archFunction = "continous", epochs = epochs),
                          boost = list( objective = "count:poisson"),
                          glm = list(family = "poisson"),
                          glm_step = list(family = "poisson")),
                       tune = "random", iters = iter,  fitSpecies = F,
                       crossValidation = crossValidation, tuningMetric = "spearmanrho",
                       balanceClasses = "None", block = T, parallel = parallel, seed = 42, keepModels = T)
    saveRDS(resultAbR, file = "Results/simAbR_GLM.RDS")
```

### With effects and w/o abundances - Network Sizes
- with strong effects (gaussian with small sd and high interaction weight)
- without species abundances 
- varying network sizes

Create Simulation:
```{r,results=FALSE}
set.seed(42)
simulatedData = simulateInteraction( main = NULL, inter = matrix(c("A1", "B1",
                                                                   "A2", "B2",
                                                                   "A3", "B3"), ncol = 2, byrow = T),
                              weights = list(inter = c(10,10,10)),
                              NumberA = 100, NumberB = 200, traitsA = c(0,6), 
                              traitsB = c(0,6),abundance = FALSE, specRange = c(0.5,1.2))
table(as.matrix(minOneInter(simulatedData$binar(1.2e-1))))
```

We tested the influence of three sizes on the performance. We set the observation time $=4e3$ to get for alomost all species at least one interaction. We sampled 25 \%, 50 \% and 100 \% of the species to get three network sizes of:

```{r,results=FALSE}
interBaseP = minOneInter(simulatedData$poisson(1.2e-1))
interBaseC = minOneInter(simulatedData$binar(1.2e-1))
smallP = interBaseP[sample(rownames(interBaseP), 0.25*length(rownames(interBaseP))),
                    sample(colnames(interBaseP), 0.25*length(colnames(interBaseP)))]
smallC = interBaseC[rownames(smallP), colnames(smallP)]

midP = interBaseP[sample(rownames(interBaseP), 0.5*length(rownames(interBaseP))),
                  sample(colnames(interBaseP), 0.5*length(colnames(interBaseP)))]
midC = interBaseC[rownames(midP), colnames(midP)]

largeP = interBaseP
largeC = interBaseC

sizeC = list(smallC = smallC, midC = midC, largeC = largeC)
sizeR = list(smallP = smallP, midP = midP, largeP = largeP)


```


Fit models with 30 random tuning steps, nested cross-validation (five-fold outer and three-fold inner). SpcCV = Leave out species with all of their interactions. AUC and Spearman evaluated tuning.
```{r,results=FALSE}
resultC = list()
if(run){
  resultC = list()
  for(i in 1:length(sizeC)){
    resultC[[i]] = runTM(createCommunity(simulatedData$A, simulatedData$B, sizeC[[i]]), 
                         method =  c( "glm", "glm_step"),  
          settings = list(dnn = list(seed = 42,  activation = "relu", drop = 0.2, archFunction = "continous", epochs = epochs),
                          cnn = list(seed = 42, activation = "relu", 
                                     drop = 0.2, nConv = 1, archFunction = "continous", epochs = epochs)),
                       tune = "random", iters = iter,  fitSpecies = F,
                       crossValidation = crossValidation, 
                       balanceClasses = "None", block = T, parallel = parallel, seed = 42, keepModels = T)
    saveRDS(resultC, file = "Results/simSizeC_GLM.RDS")
  }
  
  
  resultR = list()
  for(i in 1:length(sizeC)){
    resultR[[i]] = runTM(createCommunity(simulatedData$A, simulatedData$B, sizeR[[i]], log = F), 
                         method =  c( "glm", "glm_step"),  
          settings = list(negBin = list(seed = 42,  batch = 50, 
                                        distribution = "poisson",  archFunction = "continous", epochs = epochs),
                          boost = list( objective = "count:poisson"),
                          glm = list(family = "poisson"),
                          glm_step = list(family = "poisson")),
                       tune = "random", iters = iter,  fitSpecies = F,tuningMetric = "spearmanrho",
          crossValidation = crossValidation,
                        block = T, parallel = parallel, seed = 42, keepModels = T)
    
    saveRDS(resultR, file = "Results/simSizeR_GLM.RDS")
  }
}

```

### With effects and w/o abundances - Observation time
Varying observation times results in diffrent class distributions (classification). We choose times so, that the positive interaction had class proportions of 10 \%, 25 \% and 50 \%:

```{r,results=FALSE}
set.seed(42)
simulatedData = simulateInteraction( main = NULL, inter = matrix(c("A1", "B1",
                                                                   "A2", "B2",
                                                                   "A3", "B3"), ncol = 2, byrow = T),
                              weights = list(inter = c(10,10,10)),
                              NumberA = 100, NumberB = 200, traitsA = c(0,6), 
                              traitsB = c(0,6),abundance = FALSE, specRange = c(0.5,1.2))
table(as.matrix(minOneInter(simulatedData$binar(1.2e-1))))

obsC = list(low = minOneInter(simulatedData$binar(0.7e-2)), 
            mid = minOneInter(simulatedData$binar(3.2e-2)), 
            high = minOneInter(simulatedData$binar(1.2e-1)))

obsR = list(low = minOneInter(simulatedData$poisson(0.7e-2)), 
            mid = minOneInter(simulatedData$poisson(3.2e-2)), 
            high = minOneInter(simulatedData$poisson(1.2e-1)))
```


Fit models with 30 random tuning steps, nested cross-validation (five-fold outer and three-fold inner). SpcCV = Leave out species with all of their interactions. AUC and Spearman evaluated tuning.
```{r,results=FALSE}
if(run){
resultC = list()
  for(i in 1:length(obsC)){
    if(i != 3) bc = "Over"
    else bc = "None"
    resultC[[i]] = runTM(createCommunity(simulatedData$A, simulatedData$B, obsC[[i]]), 
                         method =  c( "glm", "glm_step"),  
          settings = list(dnn = list(seed = 42,  activation = "relu",  archFunction = "continous",  epochs = epochs),
                          cnn = list(seed = 42,  activation = "relu", 
                                     drop = 0.2, nConv = 1, archFunction = "continous", epochs = epochs)),
                       tune = "random", iters = iter,  fitSpecies = F,
                       crossValidation = crossValidation, 
                       balanceClasses = bc, block = T, parallel = parallel, seed = 42, keepModels = T)
    saveRDS(resultC, file = "Results/simObsC_GLM.RDS")
  }
  
  resultR = list()
  for(i in 1:length(obsR)){
      resultR[[i]] = runTM(createCommunity(simulatedData$A, simulatedData$B, obsR[[i]], log = F), 
                           method =  c( "glm", "glm_step"),  
          settings = list(negBin = list(seed = 42,  batch = 50, 
                                        distribution = "poisson",  archFunction = "continous", epochs = epochs),
                          boost = list( objective = "count:poisson"), 
                          glm = list(family = "poisson"),
                          glm_step = list(family = "poisson")),
                       tune = "random", iters = iter,  fitSpecies = F,tuningMetric = "spearmanrho",
          crossValidation = crossValidation,
                        block = T, parallel = parallel, seed = 42, keepModels = T)
    
    saveRDS(resultR, file = "Results/simObsR_GLM.RDS")
  }
}
```






